---
title: "1.2 - survey-wave-function"
author: "Paul Sharratt"
date: "2022-12-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1.2

Writing a function to explore the distribution of answers for a given question on each of the survey waves

Write a function to illustrate the distribution of answers for a given discrete choice question (not: questions with open text) on each of the survey waves. The function should:

• take the data frame and survey item as arguments.
• return a small multiple barplot grouped at the survey wave-level with the answer
option counts (including NAs).
• present the original survey question (label) and the variable name in the title of the plot.
• graph the value labels in the answer tick axis (i.e., in presvote16post, you would want “Hillary Clinton”,“Donald Trump”, etc., rather than the numbers representing these values)
• stop if the input variable is not a labelled <dbl+lbl> type.

Prove the correct behavior of the function with at least three survey questions.

```{r packages}
library(tidyverse)
library(janitor)
library(dplyr)
library(tidyr)
library(ggplot2)
library(haven)
library(labelled)
```


```{r loading data}

survey_df <- readRDS("../../survey/meof_usa_survey_df.RDS")
tracking_df <- readRDS("../../tracking/meof_usa_web_df.RDS")

```


```{r trying to get basic idea to work}

# return a small multiple barplot grouped at the survey wave-level with the answer
# option counts (including NAs).

survey_df_pid3 <- survey_df %>%
  select(wave, pid3, personid) %>%
  filter(pid3 != 32766 | 32767) %>%
  filter(wave == 1)

dem_count_w1 <- sum(survey_df_pid3$pid3 == 1)
rep_count_w1 <- sum(survey_df_pid3$pid3 == 2)
indp_count_w1 <- sum(survey_df_pid3$pid3 == 3)
counts <- c(dem_count_w1, rep_count_w1, indp_count_w1)
# doesn't account for the different waves.

counts_df <- as.data.frame(counts)
parties <- c("Democrat", "Republican", "Independent")
rownames(counts_df) <- parties

barplot(counts_df$counts, names.arg = parties)


```

```{r specifying for all waves & getting a small multiple barplot}

survey_df_all_waves <- survey_df %>%
  select(wave, pid3) %>%
  filter(pid3 != 32766 | 32767) %>%
  group_by(wave) %>%
  summarise(democrats = sum(pid3 == 1),
            republicans = sum(pid3 == 2),
            independents = sum(pid3 == 3))

survey_df_all_waves_long <- pivot_longer(survey_df_all_waves, c("democrats", "republicans", "independents"), names_to = "party", values_to = "count")

ggplot(data = survey_df_all_waves_long, aes(x = party, y = count)) +
  geom_bar(stat="identity") +
  facet_wrap(~wave) +  
  labs(title = "Party identification, 3 point",
       x = "Parties",
       y = "Number of Respondents")



```




   


```{r 1.2 - distribution function}

distribution_function <- function(data, item){

  item_qs <- deparse(substitute(item))  # assign item as quoted object
  
if (sum(class(data%>%pull(item_qs)) %in% c("haven_labelled", "vctrs_vctr", "double" )) == 3 )
  # checking if item_qs is <dbl+lbl> by checking class labels, can't use str() and indexing
  {
    data[[item_qs]] <- haven::as_factor(data[[item_qs]]) # using haven as_factor function 
    ggplot(data,     # creating a small multiples plot
           aes(x = {{item}})) + # passing unquoted variables using {{}}
      geom_bar() +
      scale_x_discrete() +
      theme_test() +
      coord_flip() +
      labs(title = paste0(attributes(survey_df[[item_qs]])$label), # using 'label' from item_qs attributes for title
       x = item_qs, 
       y = "Number of respondents") +
      facet_wrap(~wave, nrow = 3) 
    } else {
      stop("The input variable is not a labelled <dbl+lbl> type.")
      }
}

distribution_function(survey_df, pid3)

distribution_function (survey_df, approval_trump)

distribution_function (survey_df, ideo5)


class(survey_df$pid3)

```





