---
title: "1.3 - netflix-activity"
author: "Niklas Pawelzik"
date: "2022-12-19"
output: html_document
---


## Task 1.3: Distribution of Netflix activity throughout the day by the weekday


Illustrate with a ridgeplot the distribution of Netflix activity throughout the day by 
weekday following good practice of visualizations. For this plot you should:

• match each respondent with their first logged state of residence in the survey.
• update the time of each web activity based on the user‘s home state and the 
respective time zone in times_zones.RDS.
• add vertical lines at the quartiles.
• provide a title and description, making it a standalone figure that speaks for itself.

```{r}
## 1
# load packages
library(tidyverse)
library(janitor)
library(lubridate)
library(ggplot2)
library(ggridges)
```

```{r}
## 2
# load data
survey_df <- readRDS("../../survey/meof_usa_survey_df.RDS")
tracking_df <- readRDS("../../tracking/meof_usa_web_df.RDS")%>% select(-country)
time_zones_df <- readRDS("../../time_zones/time_zones.RDS")
```

```{r}
## 3
## rename state as in timezones df
survey_df$inputstate <- 
  case_when(survey_df$inputstate == 1 ~ "Alabama",
            survey_df$inputstate == 2 ~ "Alaska",
            survey_df$inputstate == 4 ~ "Arizona",
            survey_df$inputstate == 5 ~ "Arkansas",
            survey_df$inputstate == 6 ~ "California",
            survey_df$inputstate == 8 ~ "Colorado",
            survey_df$inputstate == 9 ~ "Connecticut",
            survey_df$inputstate == 10 ~ "Delaware",
            survey_df$inputstate == 11 ~ "District of Columbia",
            survey_df$inputstate == 12 ~ "Florida",
            survey_df$inputstate == 13 ~ "Georgia",
            survey_df$inputstate == 15 ~ "Hawaii",
            survey_df$inputstate == 16 ~ "Idaho",
            survey_df$inputstate == 17 ~ "Illinois",
            survey_df$inputstate == 18 ~ "Indiana",
            survey_df$inputstate == 19 ~ "Iowa",
            survey_df$inputstate == 20 ~ "Kansas",
            survey_df$inputstate == 21 ~ "Kentucky",
            survey_df$inputstate == 22 ~ "Louisiana",
            survey_df$inputstate == 23 ~ "Maine",
            survey_df$inputstate == 24 ~ "Maryland",
            survey_df$inputstate == 25 ~ "Massachusetts",
            survey_df$inputstate == 26 ~ "Michigan",
            survey_df$inputstate == 27 ~ "Minnesota",
            survey_df$inputstate == 28 ~ "Mississippi",
            survey_df$inputstate == 29 ~ "Missouri",
            survey_df$inputstate == 30 ~ "Montana",
            survey_df$inputstate == 31 ~ "Nebraska",
            survey_df$inputstate == 32 ~ "Nevada",
            survey_df$inputstate == 33 ~ "New Hampshire",
            survey_df$inputstate == 34 ~ "New Jersey",
            survey_df$inputstate == 35 ~ "New Mexico",
            survey_df$inputstate == 36 ~ "New York",
            survey_df$inputstate == 37 ~ "North Carolina",
            survey_df$inputstate == 38 ~ "North Dakota",
            survey_df$inputstate == 39 ~ "Ohio",
            survey_df$inputstate == 40 ~ "Oklahoma",
            survey_df$inputstate == 41 ~ "Oregon",
            survey_df$inputstate == 42 ~ "Pennsylvania",
            survey_df$inputstate == 44 ~ "Rhode Island",
            survey_df$inputstate == 45 ~ "South Carolina",
            survey_df$inputstate == 46 ~ "South Dakota",
            survey_df$inputstate == 47 ~ "Tennessee",
            survey_df$inputstate == 48 ~ "Texas",
            survey_df$inputstate == 49 ~ "Utah",
            survey_df$inputstate == 50 ~ "Vermont",
            survey_df$inputstate == 51 ~ "Virginia",
            survey_df$inputstate == 53 ~ "Washington",
            survey_df$inputstate == 54 ~ "West Virginia",
            survey_df$inputstate == 55 ~ "Wisconsin",
            survey_df$inputstate == 56 ~ "Wyoming",
            survey_df$inputstate == 60 ~ "American Samoa",
            survey_df$inputstate == 64 ~ "Federated States of Micronesia",
            survey_df$inputstate == 66 ~ "Guam",
            survey_df$inputstate == 68 ~ "Marshall Islands",
            survey_df$inputstate == 69 ~ "Northern Mariana Islands",
            survey_df$inputstate == 70 ~ "Palau",
            survey_df$inputstate == 72 ~ "Puerto Rico",
            survey_df$inputstate == 74 ~ "U.S. Minor Outlying Islands",
            survey_df$inputstate == 78 ~ "Virgin Islands",
            survey_df$inputstate == 81 ~ "Alberta",
            survey_df$inputstate == 82 ~ "British Columbia",
            survey_df$inputstate == 83 ~ "Manitoba",
            survey_df$inputstate == 84 ~ "New Brunswick",
            survey_df$inputstate == 85 ~ "Newfoundland",
            survey_df$inputstate == 86 ~ "Northwest Territories",
            survey_df$inputstate == 87 ~ "Nova Scotia",
            survey_df$inputstate == 88 ~ "Nunavut",
            survey_df$inputstate == 89 ~ "Ontario",
            survey_df$inputstate == 90 ~ "Prince Edward Island",
            survey_df$inputstate == 91 ~ "Quebec",
            survey_df$inputstate == 92 ~ "Saskatchewan",
            survey_df$inputstate == 93 ~ "Yukon Territory")

```

```{r}
## 4
# identify first logged state of residence in the survey
## filter for one match per "personid", displaying the lowest number of "wave" for which we have a value in "inputstate" 
earliest_inputstate <- survey_df %>%
  filter(!is.na(inputstate))%>%
  group_by(personid)%>%
  arrange(wave) %>%
  slice(1) %>%
  ungroup() %>%
  select(personid, inputstate)

# update the time of each web activity based on the user‘s home state and the respective time zone in times_zones.RDS

earliest_inputstate <- earliest_inputstate %>% 
    rename("state" = "inputstate")

earliest_inputstate <- merge(x=earliest_inputstate, y=time_zones_df, by= "state", all.x=TRUE)

```

```{r}
## 5
# search for netflix use and create data frame
netflix_use <- tracking_df[tracking_df$domain=='netflix' | grepl('netflix',tracking_df$domain), ]

netflix_use <- merge(x=netflix_use, y=earliest_inputstate, by= "personid", all.x=TRUE)
```

```{r}
## 6
# set duration to "second" instead of minutes
netflix_use$duration <- netflix_use$duration * 60
# create end_date column
netflix_use$stopped_use_at <- netflix_use$used_at + netflix_use$duration
# create weekday column
netflix_use$weekday_used <- weekdays(netflix_use$used_at)

# rename weekdays
netflix_use$weekday_used[netflix_use$weekday_used == 'Montag'] <- 'Monday'
netflix_use$weekday_used[netflix_use$weekday_used == 'Dienstag'] <- 'Tuesday'
netflix_use$weekday_used[netflix_use$weekday_used == 'Mittwoch'] <- 'Wednesday'
netflix_use$weekday_used[netflix_use$weekday_used == 'Donnerstag'] <- 'Thursday'
netflix_use$weekday_used[netflix_use$weekday_used == 'Freitag'] <- 'Friday'
netflix_use$weekday_used[netflix_use$weekday_used == 'Samstag'] <- 'Saturday'
netflix_use$weekday_used[netflix_use$weekday_used == 'Sonntag'] <- 'Sunday'

# isolate_day_time_hour
netflix_use$hour_used <- hour(netflix_use$used_at)

# isolate_day_time_minute
netflix_use$minute_used <- minute(netflix_use$used_at)

# isolate_day_time_second
netflix_use$second_used <- second(netflix_use$used_at)

netflix_use$day_time_used <- hms(paste(netflix_use$hour_used, netflix_use$minute_used, netflix_use$second_used, sep = ":"))

netflix_use$day_time_used_2 <- hms::as_hms(netflix_use$used_at)

netflix_use$day_time_used_local_time_2 <- hms::as_hms(netflix_use$used_at_local_time)

```

```{r}
## 7
# change UTC to state time zones
# (Credit to fellow-student Armin, function comes from him):
local_time <- Vectorize(function(x,y){format(x, tz=y, usetz=TRUE)})

netflix_use <- netflix_use %>%
  mutate(
    used_at_local_time = map2(.x = used_at, .y = time_zone, .f = local_time)
  )

netflix_use <- netflix_use %>%
  unnest(used_at_local_time)

netflix_use$used_at_local_time <- as.POSIXct(netflix_use$used_at_local_time, format = "%Y-%m-%d %H:%M:%S")
```

```{r}
##8
netflix_use$adapted_dates <- as.POSIXct(netflix_use$day_time_used_2, tz = netflix_use$time_zone)
# %>% hms::as_hms()

#restate required variable day_time_used_local_time_2
netflix_use$day_time_used_local_time_2 <- hms::as_hms(netflix_use$used_at_local_time)


# netflix_use$weekday_used <- weekdays(netflix_use$adapted_dates, origin = netflix_use$time_zone)

```


```{r}
## 9
# Plotting
## NOTE: As we were not perfectly clear about how to understand the time-zone part of the exercise, below we provide two plots for comparison:
# One of them ("Times as Provided in Dataframe") uses the original times as indicated under used_at in the tracking dataset.
# The other ("Times Changed According to Timezones Provided") uses the times according to the respective state of residence of the user.
# Indicative for the difference is also the difference in peak Netflix time:  The first one has more evenly distributed peaks throughout the day, as different users in different time zones tend to use Netflix at different times. The second plot shows the uniform peak of Netflix access at "primetime" in the evening, roughly speaking between 6 p.m. and 11 p.m.

ggplot(netflix_use, aes(x = day_time_used_local_time_2, y = weekday_used, fill = factor(stat(quantile)))) +
  # geom_density_ridges(scale = 1) +
  # adding vertical lines at the quartiles
  stat_density_ridges(geom = "density_ridges_gradient", quantile_lines = TRUE,  calc_ecdf = TRUE) +
  scale_x_continuous(limits = c(0, 86399), n.breaks = 5, breaks = c(0, 86399*0.25, 86399*0.5, 86399*0.75, 86399-60), label = c( "00:00", "06:00", "12:00", "18:00", "23:59")) +
  scale_y_discrete(labels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")) +
  theme_minimal() +
  labs(title = 'Times Changed According to Timezones Provided') +
  xlab("Time of the Day") + 
  ylab("Day of the Week") +
  scale_fill_viridis_d(name = "Quartiles")

ggplot(netflix_use, aes(x = day_time_used_2, y = weekday_used, fill = factor(stat(quantile)))) +
  # geom_density_ridges(scale = 1) +
  # adding vertical lines at the quartiles
  stat_density_ridges(geom = "density_ridges_gradient", quantile_lines = TRUE,  calc_ecdf = TRUE) +
  # scale_x_datetime(date_breaks = "2 hours", date_labels = "%h") +
  scale_x_continuous(limits = c(0, 86399), n.breaks = 5, breaks = c(0, 86399*0.25, 86399*0.5, 86399*0.75, 86399-60), label = c( "00:00", "06:00", "12:00", "18:00", "23:59")) +
  scale_y_discrete(labels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")) +
  theme_minimal() +
  labs(title = 'Times as Provided in Dataframe') +
  xlab("Time of the Day") + 
  ylab("Day of the Week") +
  scale_fill_viridis_d(name = "Quartiles")
```