---
title: "1.4 - Interactive_survey_map"
author: "Justus v. Samson-Himmelstjerna"
date: "2022-12-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(zoo)
library(leaflet)
library(leaflet.extras)
library(geojsonio)
```

## Task 1.4 - Interactive map of survey entries

Create an interactive leaflet map divided by states that are colored in relation to a
total number of survey responses across all waves, following good practice of
visualization. For this plot you should:

• employ a color palette based on the number range of survey entries.

• use the Stamen.Toner tile.

• create a popup that reads “Total survey responses for (State initials): (Number)”.

```{r load data}
# load data
survey_df <- readRDS("../../survey/meof_usa_survey_df.RDS")
```

```{r clean data}
# clean data in order to account for NAs in inputsate for people who most likely did not move in the meantime since they have only stated on state of residence

fill_na <- function(x) {
  # Check if the person has given exactly one state in the inputstate column
  if (n_distinct(x) == 2) {
    # Check if the person has given an NA in a later wave
    if (any(is.na(x))) {
      # Forward fill the NA values with the previous value in the inputstate column
      x <- na.locf(x)
    }
  }
  return(x)
}

# Group the dataframe by personid and apply the custom function to the inputstate column
survey_df_cleaned <- survey_df %>%
  group_by(personid) %>%
  mutate(inputstate = fill_na(inputstate)) %>%
  ungroup()
```

```{r survey responses}
# Get the total number of survey responses by state
survey_by_state <- survey_df_cleaned %>% 
  group_by(inputstate) %>% 
  summarise(total_responses = n()) %>% 
  drop_na(inputstate)

# change numbers to state names
survey_by_state$inputstate <- 
  case_when(survey_by_state$inputstate == 1 ~ "Alabama",
            survey_by_state$inputstate == 2 ~ "Alaska",
            survey_by_state$inputstate == 4 ~ "Arizona",
            survey_by_state$inputstate == 5 ~ "Arkansas",
            survey_by_state$inputstate == 6 ~ "California",
            survey_by_state$inputstate == 8 ~ "Colorado",
            survey_by_state$inputstate == 9 ~ "Connecticut",
            survey_by_state$inputstate == 10 ~ "Delaware",
            survey_by_state$inputstate == 11 ~ "District of Columbia",
            survey_by_state$inputstate == 12 ~ "Florida",
            survey_by_state$inputstate == 13 ~ "Georgia",
            survey_by_state$inputstate == 15 ~ "Hawaii",
            survey_by_state$inputstate == 16 ~ "Idaho",
            survey_by_state$inputstate == 17 ~ "Illinois",
            survey_by_state$inputstate == 18 ~ "Indiana",
            survey_by_state$inputstate == 19 ~ "Iowa",
            survey_by_state$inputstate == 20 ~ "Kansas",
            survey_by_state$inputstate == 21 ~ "Kentucky",
            survey_by_state$inputstate == 22 ~ "Louisiana",
            survey_by_state$inputstate == 23 ~ "Maine",
            survey_by_state$inputstate == 24 ~ "Maryland",
            survey_by_state$inputstate == 25 ~ "Massachusetts",
            survey_by_state$inputstate == 26 ~ "Michigan",
            survey_by_state$inputstate == 27 ~ "Minnesota",
            survey_by_state$inputstate == 28 ~ "Mississippi",
            survey_by_state$inputstate == 29 ~ "Missouri",
            survey_by_state$inputstate == 30 ~ "Montana",
            survey_by_state$inputstate == 31 ~ "Nebraska",
            survey_by_state$inputstate == 32 ~ "Nevada",
            survey_by_state$inputstate == 33 ~ "New Hampshire",
            survey_by_state$inputstate == 34 ~ "New Jersey",
            survey_by_state$inputstate == 35 ~ "New Mexico",
            survey_by_state$inputstate == 36 ~ "New York",
            survey_by_state$inputstate == 37 ~ "North Carolina",
            survey_by_state$inputstate == 38 ~ "North Dakota",
            survey_by_state$inputstate == 39 ~ "Ohio",
            survey_by_state$inputstate == 40 ~ "Oklahoma",
            survey_by_state$inputstate == 41 ~ "Oregon",
            survey_by_state$inputstate == 42 ~ "Pennsylvania",
            survey_by_state$inputstate == 44 ~ "Rhode Island",
            survey_by_state$inputstate == 45 ~ "South Carolina",
            survey_by_state$inputstate == 46 ~ "South Dakota",
            survey_by_state$inputstate == 47 ~ "Tennessee",
            survey_by_state$inputstate == 48 ~ "Texas",
            survey_by_state$inputstate == 49 ~ "Utah",
            survey_by_state$inputstate == 50 ~ "Vermont",
            survey_by_state$inputstate == 51 ~ "Virginia",
            survey_by_state$inputstate == 53 ~ "Washington",
            survey_by_state$inputstate == 54 ~ "West Virginia",
            survey_by_state$inputstate == 55 ~ "Wisconsin",
            survey_by_state$inputstate == 56 ~ "Wyoming",
            survey_by_state$inputstate == 60 ~ "American Samoa",
            survey_by_state$inputstate == 64 ~ "Federated States of Micronesia",
            survey_by_state$inputstate == 66 ~ "Guam",
            survey_by_state$inputstate == 68 ~ "Marshall Islands",
            survey_by_state$inputstate == 69 ~ "Northern Mariana Islands",
            survey_by_state$inputstate == 70 ~ "Palau",
            survey_by_state$inputstate == 72 ~ "Puerto Rico",
            survey_by_state$inputstate == 74 ~ "U.S. Minor Outlying Islands",
            survey_by_state$inputstate == 78 ~ "Virgin Islands",
            survey_by_state$inputstate == 81 ~ "Alberta",
            survey_by_state$inputstate == 82 ~ "British Columbia",
            survey_by_state$inputstate == 83 ~ "Manitoba",
            survey_by_state$inputstate == 84 ~ "New Brunswick",
            survey_by_state$inputstate == 85 ~ "Newfoundland",
            survey_by_state$inputstate == 86 ~ "Northwest Territories",
            survey_by_state$inputstate == 87 ~ "Nova Scotia",
            survey_by_state$inputstate == 88 ~ "Nunavut",
            survey_by_state$inputstate == 89 ~ "Ontario",
            survey_by_state$inputstate == 90 ~ "Prince Edward Island",
            survey_by_state$inputstate == 91 ~ "Quebec",
            survey_by_state$inputstate == 92 ~ "Saskatchewan",
            survey_by_state$inputstate == 93 ~ "Yukon Territory")

# Create a new column for State initials
survey_by_state$state_initials <- map_chr(survey_by_state$inputstate,
                                        ~state.abb[match(.x, state.name)])
# Adding DC since it had ben dropped for some reason
survey_by_state$state_initials[9] <- "DC"

# loading the data from JSON on US states
states <- geojsonio::geojson_read("https://rstudio.github.io/leaflet/json/us-states.geojson", what = "sp")
```

```{r interactive leaflet map}
# Create a color palette based on the number range of survey entries
color_palette <- colorQuantile("YlOrRd", survey_by_state$total_responses,
                               n = 9)

# Create an interactive leaflet map divided by states
leaflet(data = survey_by_state) %>%
  addProviderTiles(providers$Stamen.Toner) %>%
   addPolygons(data = states, 
               fillColor = ~color_palette(survey_by_state$total_responses),
               color = "white", weight = 0.5,
              popup = paste("Total survey responses for",
                            survey_by_state$state_initials,
                            ":",
                            survey_by_state$total_responses))
# since the colorQuantile function is only able to give a legend as probability ranges in percentage (which I find confusing) therefore I have decided to not include a legend. The other option would be to use colorNumeric, however, this has the downside of giving a smaller colour range. This would decrease the informational value of the map in my opinion.```